---
title: "indiv smooths"
author: "Megan Lott"
date: "10/14/2020"
output: html_document
---

Load all required libraries.
```{r}
library(tidyverse)
library(plotly)
library(broom)
```

Read in raw data from RDS.
```{r}
raw_data <- readRDS("./n1_n2_cleaned_cases.rds")
```

Make a few small modifications to names and data for visualizations.
```{r}
final_data <- raw_data %>% mutate(log_copy_per_L = log10(mean_copy_num_L)) %>%
  rename(Facility = wrf) %>%
  mutate(Facility = recode(Facility, 
                           "NO" = "WRF A",
                           "MI" = "WRF B",
                           "CC" = "WRF C"))
```


Seperate the data by gene target to ease layering in the final plot
```{r}
#make three data layers
only_positives <<- subset(final_data, (!is.na(final_data$Facility)))
only_n1 <- subset(only_positives, target == "N1")
only_n2 <- subset(only_positives, target == "N2")
only_background <<-final_data %>% 
  select(c(date, cases_cum_clarke, new_cases_clarke, X7_day_ave_clarke, cases_per_100000_clarke)) %>%
  group_by(date) %>% summarise_if(is.numeric, mean)

#specify fun colors
background_color <- "#7570B3"
seven_day_ave_color <- "#E6AB02"
marker_colors <- c("N1" = '#1B9E77',"N2" ='#D95F02')
    
```

```{r}

#remove facilty C for now
#only_n1 <- only_n1[!(only_n1$Facility == "WRF C"),]
#only_n2 <- only_n2[!(only_n2$Facility == "WRF C"),]

only_n1 <- only_n1[!(only_n1$Facility == "WRF A" & only_n1$date == "2020-11-02"), ]
only_n2 <- only_n2[!(only_n2$Facility == "WRF A" & only_n2$date == "2020-11-02"), ]

```


Build the main plot
```{r}

      #first layer is the background epidemic curve
        p1 <- only_background %>%
              plotly::plot_ly() %>%
              plotly::add_trace(x = ~date, y = ~new_cases_clarke, 
                                type = "bar", 
                                hoverinfo = "text",
                                text = ~paste('</br> Date: ', date,
                                                     '</br> Daily Cases: ', new_cases_clarke),
                                alpha = 0.5,
                                name = "Daily Reported Cases",
                                color = background_color,
                                colors = background_color,
                                showlegend = FALSE) %>%
            layout(yaxis = list(title = "Clarke County Daily Cases", showline=TRUE)) %>%
            layout(legend = list(orientation = "h", x = 0.2, y = -0.3))
        
        #renders the main plot layer two as seven day moving average
        p1 <- p1 %>% plotly::add_trace(x = ~date, y = ~X7_day_ave_clarke, 
                             type = "scatter",
                             mode = "lines",
                             hoverinfo = "text",
                            text = ~paste('</br> Date: ', date,
                                                     '</br> Seven-Day Moving Average: ', X7_day_ave_clarke),
                             name = "Seven Day Moving Average Athens",
                             line = list(color = seven_day_ave_color),
                             showlegend = FALSE)
      

        
        #renders the main plot layer three as positive target hits
        
        p2 <- plotly::plot_ly() %>%
          plotly::add_trace(x = ~date, y = ~mean_copy_num_L,
                                       type = "scatter",
                                       mode = "markers",
                                       hoverinfo = "text",
                                       text = ~paste('</br> Date: ', date,
                                                     '</br> Facility: ', Facility,
                                                     '</br> Target: ', target,
                                                     '</br> Copies/L: ', round(mean_copy_num_L, digits = 2)),
                                       data = only_n1,
                                       symbol = ~Facility,
                                       marker = list(color = '#1B9E77', size = 8, opacity = 0.65),
                                       showlegend = FALSE) %>%
          plotly::add_trace(x = ~date, y = ~mean_copy_num_L,
                                       type = "scatter",
                                       mode = "markers",
                                       hoverinfo = "text",
                                       text = ~paste('</br> Date: ', date,
                                                     '</br> Facility: ', Facility,
                                                     '</br> Target: ', target,
                                                     '</br> Copies/L: ', round(mean_copy_num_L, digits = 2)),
                                       data = only_n2,
                                       symbol = ~Facility,
                                       marker = list(color = '#D95F02', size = 8, opacity = 0.65),
                                       showlegend = FALSE) %>%
            layout(yaxis = list(title = "SARS CoV-2 Copies/L", 
                                 showline = TRUE,
                                 type = "log",
                                 dtick = 1,
                                 automargin = TRUE)) %>%
            layout(legend = list(orientation = "h", x = 0.2, y = -0.3))
        
        #adds the limit of detection dashed line
        p2 <- p2 %>% plotly::add_segments(x = as.Date("2020-03-14"), 
                                          xend = ~max(date + 10), 
                                          y = 3571.429, yend = 3571.429,
                                          opacity = 0.35,
                                          line = list(color = "black", dash = "dash")) %>%
          layout(annotations = list(x = as.Date("2020-03-28"), y = 3.8, xref = "x", yref = "y", 
                                    text = "Limit of Detection", showarrow = FALSE))

        

        p1
        p2
        
```
Combine the two main plot pieces as a subplot

```{r}
p_combined <-
    plotly::subplot(p2,p1, # plots to combine, top to bottom
      nrows = 2,
      heights = c(.6,.4),  # relative heights of the two plots
      shareX = TRUE,  # plots will share an X axis
      titleY = TRUE
    ) %>%
    # create a vertical "spike line" to compare data across 2 plots
    plotly::layout(
      xaxis = list(
        spikethickness = 1,
        spikedash = "dot",
        spikecolor = "black",
        spikemode = "across+marker",
        spikesnap = "cursor"
      ),
      yaxis = list(spikethickness = 0)
    )
p_combined
```

Save the plot to pull into the index
```{r}
#save(p_combined, file = "./plotly_fig.rda")
```

Save an htmlwidget for website embedding
```{r}
#htmlwidgets::saveWidget(p_combined, "plotly_fig.html")
```


```{r}
#seperate n1 and n2 frames by site
#n1
wrf_a_only_n1 <- subset(only_n1, Facility == "WRF A")
wrf_b_only_n1 <- subset(only_n1, Facility == "WRF B")
wrf_c_only_n1 <- subset(only_n1, Facility == "WRF C")

#n2
wrf_a_only_n2 <- subset(only_n2, Facility == "WRF A")
wrf_b_only_n2 <- subset(only_n2, Facility == "WRF B")
wrf_c_only_n2 <- subset(only_n2, Facility == "WRF C")

```

```{r}
#build a function here to make smooth frames so we don't repeat everything in huge loops
#FOR INDIVIDUAL FIGURES ONLY
make_n1_smooth_frame <- function(df){
  smooth_n1 <- df %>% select(-c(Facility)) %>% 
  group_by(date, cases_cum_clarke, new_cases_clarke, X7_day_ave_clarke, cases_per_100000_clarke) %>%
  summarize(sum_copy_num_L = sum(mean_total_copies)) %>%
  ungroup() %>%
  mutate(log_sum_copies_L = log10(sum_copy_num_L)) %>%
  mutate(target = "N1")
  return(smooth_n1)
}

make_n2_smooth_frame <- function(df){
  smooth_n1 <- df %>% select(-c(Facility)) %>% 
  group_by(date, cases_cum_clarke, new_cases_clarke, X7_day_ave_clarke, cases_per_100000_clarke) %>%
  summarize(sum_copy_num_L = sum(mean_total_copies)) %>%
  ungroup() %>%
  mutate(log_sum_copies_L = log10(sum_copy_num_L)) %>%
  mutate(target = "N2")
  return(smooth_n1)
}

#run frames through the functions
wrfa_smooth_n1 <- make_n1_smooth_frame(wrf_a_only_n1)
wrfb_smooth_n1 <- make_n1_smooth_frame(wrf_b_only_n1)
wrfc_smooth_n1 <- make_n1_smooth_frame(wrf_c_only_n1)

wrfa_smooth_n2 <- make_n2_smooth_frame(wrf_a_only_n2)
wrfb_smooth_n2 <- make_n2_smooth_frame(wrf_b_only_n2)
wrfc_smooth_n2 <- make_n2_smooth_frame(wrf_c_only_n2)

#get max date
maxdate <- max(wrfa_smooth_n1$date)
mindate <- min(wrfa_smooth_n1$date)

```


Build loess smoothing figures figures

```{r}
#COMBINED FIGURE ONLY
#create smoothing data frames 
#n1
smooth_n1 <- only_n1 %>% select(-c(Facility)) %>% 
  group_by(date, cases_cum_clarke, new_cases_clarke, X7_day_ave_clarke, cases_per_100000_clarke) %>%
  summarize(sum_copy_num_L = sum(mean_total_copies)) %>%
  ungroup() %>%
  mutate(log_sum_copies_L = log10(sum_copy_num_L)) %>%
  mutate(target = "N1")

#n2
smooth_n2 <- only_n2 %>% select(-c(Facility)) %>% 
  group_by(date, cases_cum_clarke, new_cases_clarke, X7_day_ave_clarke, cases_per_100000_clarke) %>%
  summarize(sum_copy_num_L = sum(mean_total_copies)) %>%
  ungroup() %>%
  mutate(log_sum_copies_L = log10(sum_copy_num_L)) %>%
  mutate(target = "N2")
```

```{r}
#**************************************COMBINED PLOT**********************************************
#add trendlines 
#extract data from geom_smooth
#n1 extract
# *********************************span 0.6***********************************
#*****************Must always update the n = TOTAL NUMBER OF DAYS*************************
extract_n1 <- ggplot(smooth_n1, aes(x = date, y = log_sum_copies_L)) + 
  stat_smooth(aes(outfit=fit_n1<<-..y..), method = "loess", color = '#1B9E77', 
              span = 0.6, n = 142)
#n2 extract
extract_n2 <- ggplot(smooth_n2, aes(x = date, y = log_sum_copies_L)) + 
  stat_smooth(aes(outfit=fit_n2<<-..y..), method = "loess", color = '#1B9E77', 
              span = 0.6, n = 142)

#look at the fits to align dates and total observations
#n1
extract_n1
fit_n1
#n2
extract_n2
fit_n2

#assign fits to a vector
n1_trend <- fit_n1
n2_trend <- fit_n2

#extract y min and max for each
limits_n1 <- ggplot_build(extract_n1)$data
limits_n1 <- as.data.frame(limits_n1)
n1_ymin <- limits_n1$ymin
n1_ymax <- limits_n1$ymax

limits_n2 <- ggplot_build(extract_n2)$data
limits_n2 <- as.data.frame(limits_n2)
n2_ymin <- limits_n2$ymin
n2_ymax <- limits_n2$ymax

#reassign dataframes (just to be safe)
work_n1 <- smooth_n1
work_n2 <- smooth_n2

#fill in missing dates to smooth fits
work_n1 <- work_n1 %>% complete(date = seq(min(date), max(date), by = "1 day"))
date_vec_n1 <- work_n1$date
work_n2 <- work_n2 %>% complete(date = seq(min(date), max(date), by = "1 day"))
date_vec_n2 <- work_n2$date

#create a new smooth dataframe to layer
smooth_frame_n1 <- data.frame(date_vec_n1, n1_trend, n1_ymin, n1_ymax)
smooth_frame_n2 <- data.frame(date_vec_n2, n2_trend, n2_ymin, n2_ymax)

```

```{r}
#make plotlys
#**************************************COMBINED PLOT**********************************************
#plot smooth frames
p3 <- plotly::plot_ly() %>%
  plotly::add_lines(x = ~date_vec_n1, y = ~n1_trend,
                    data = smooth_frame_n1,
                    hoverinfo = "text",
                    text = ~paste('</br> Date: ', date_vec_n1,
                                  '</br> Median Log Copies: ', round(n1_trend, digits = 2),
                                  '</br> Target: N1'),
                    line = list(color = '#1B9E77', size = 8, opacity = 0.65),
                    showlegend = FALSE) %>%
plotly::add_lines(x = ~date_vec_n2, y = ~n2_trend,
                  data = smooth_frame_n2,
                    hoverinfo = "text",
                    text = ~paste('</br> Date: ', date_vec_n2,
                                  '</br> Median Log Copies: ', round(n2_trend, digits = 2),
                                  '</br> Target: N2'),
                    line = list(color = '#D95F02', size = 8, opacity = 0.65),
                    showlegend = FALSE) %>%
plotly::add_ribbons(x ~date_vec_n1, ymin = ~n1_ymin, ymax = ~n1_ymax,
                    showlegend = FALSE,
                    opacity = 0.25,
                    hoverinfo = "text",
                    text = ~paste('</br> Date: ', date_vec_n1, #leaving in case we want to change
                                  '</br> Max Log Copies: ', round(n1_ymax, digits = 2),
                                  '</br> Min Log Copies: ', round(n1_ymin, digits = 2),
                                  '</br> Target: N1'),
                    name = "",
                    line = list(color = '#1B9E77')) %>%
plotly::add_ribbons(x ~date_vec_n2, ymin = ~n2_ymin, ymax = ~n2_ymax,
                    showlegend = FALSE,
                    opacity = 0.25,
                    hoverinfo = "text",
                    text = ~paste('</br> Date: ', date_vec_n2, #leaving in case we want to change
                                  '</br> Max Log Copies: ', round(n2_ymax, digits = 2),
                                  '</br> Min Log Copies: ', round(n2_ymin, digits = 2),
                                  '</br> Target: N2'),
                    name = "",
                    line = list(color = '#D95F02')) %>%
                layout(yaxis = list(title = "Total Log SARS CoV-2 Copies", 
                                 showline = TRUE,
                                 automargin = TRUE)) %>%
                layout(xaxis = list(title = "Date")) %>%
    plotly::add_segments(x = as.Date("2020-06-24"), 
                                          xend = as.Date("2020-06-24"), 
                                          y = ~min(n1_ymin), yend = ~max(n1_ymax),
                                          opacity = 0.35,
                                          name = "Bars Repoen",
                                          hoverinfo = "text",
                                          text = "</br> Bars Reopen",
                                                 "</br> 2020-06-24",
                                          showlegend = FALSE,
                                          line = list(color = "black", dash = "dash")) %>%
    plotly::add_segments(x = as.Date("2020-07-09"), 
                                          xend = as.Date("2020-07-09"), 
                                          y = ~min(n1_ymin), yend = ~max(n1_ymax),
                                          opacity = 0.35,
                                          name = "Mask Mandate",
                                          hoverinfo = "text",
                                          text = "</br> Mask Mandate",
                                                 "</br> 2020-07-09",
                                          showlegend = FALSE,
                                          line = list(color = "black", dash = "dash")) %>%
    plotly::add_segments(x = as.Date("2020-08-20"), 
                                          xend = as.Date("2020-08-20"), 
                                          y = ~min(n1_ymin), yend = ~max(n1_ymax),
                                          opacity = 0.35,
                                          name = "</br> Classes Begin",
                                                 "</br> 2020-08-20",
                                          hoverinfo = "text",
                                          text = "Classes Begin",
                                          showlegend = FALSE,
                                          line = list(color = "black", dash = "dash")) %>%
  plotly::add_markers(x = ~date, y = ~log_sum_copies_L,
                      data = smooth_n1,
                       hoverinfo = "text",
                       showlegend = FALSE,
                       text = ~paste('</br> Date: ', date, 
                                     '</br> Actual Log Copies: ', round(log_sum_copies_L, digits = 2)),
                       marker = list(color = '#1B9E77', size = 6, opacity = 0.65)) %>%
    plotly::add_markers(x = ~date, y = ~log_sum_copies_L,
                      data = smooth_n2,
                       hoverinfo = "text",
                       showlegend = FALSE,
                       text = ~paste('</br> Date: ', date, 
                                     '</br> Actual Log Copies: ', round(log_sum_copies_L, digits = 2)),
                       marker = list(color = '#D95F02', size = 6, opacity = 0.65))

p3
```

Create final trend plot by stacking with epidemic curve

```{r}
smooth_extracttest <-
    plotly::subplot(p3,p1, # plots to combine, top to bottom
      nrows = 2,
      heights = c(.6,.4),  # relative heights of the two plots
      shareX = TRUE,  # plots will share an X axis
      titleY = TRUE
    ) %>%
    # create a vertical "spike line" to compare data across 2 plots
    plotly::layout(
      xaxis = list(
        spikethickness = 1,
        spikedash = "dot",
        spikecolor = "black",
        spikemode = "across+marker",
        spikesnap = "cursor"
      ),
      yaxis = list(spikethickness = 0)
    )

smooth_extracttest
```

```{r}
#save(smooth_extracttest, file = "./smooth_extracttest.rda")
```





######### This makes the individual plots

```{r}
#**************************************WRF A PLOT**********************************************
#add trendlines 
#extract data from geom_smooth
#n1 extract
# *********************************span 0.6***********************************
#*****************Must always update the n = TOTAL NUMBER OF DAYS*************************
extract_n1a <- ggplot(wrfa_smooth_n1, aes(x = date, y = log_sum_copies_L)) + 
  stat_smooth(aes(outfit=fit_n1a<<-..y..), method = "loess", color = '#1B9E77', 
              span = 0.6, n = 142)
#n2 extract
extract_n2a <- ggplot(wrfa_smooth_n2, aes(x = date, y = log_sum_copies_L)) + 
  stat_smooth(aes(outfit=fit_n2a<<-..y..), method = "loess", color = '#1B9E77', 
              span = 0.6, n = 142)

#look at the fits to align dates and total observations
#n1
extract_n1a
fit_n1a
#n2
extract_n2a
fit_n2a

#assign fits to a vector
n1_trenda <- fit_n1a
n2_trenda <- fit_n2a

#extract y min and max for each
limits_n1a <- ggplot_build(extract_n1a)$data
limits_n1a <- as.data.frame(limits_n1a)
n1_ymina <- limits_n1a$ymin
n1_ymaxa <- limits_n1a$ymax

limits_n2a <- ggplot_build(extract_n2a)$data
limits_n2a <- as.data.frame(limits_n2a)
n2_ymina <- limits_n2a$ymin
n2_ymaxa <- limits_n2a$ymax

#reassign dataframes (just to be safe)
work_n1a <- wrfa_smooth_n1
work_n2a<- wrfa_smooth_n1

#fill in missing dates to smooth fits
work_n1a <- work_n1a %>% complete(date = seq(min(date), max(date), by = "1 day"))
date_vec_n1a <- work_n1a$date
work_n2a <- work_n2a %>% complete(date = seq(min(date), max(date), by = "1 day"))
date_vec_n2a <- work_n2a$date

#create a new smooth dataframe to layer
smooth_frame_n1a <- data.frame(date_vec_n1a, n1_trenda, n1_ymina, n1_ymaxa)
smooth_frame_n2a <- data.frame(date_vec_n2a, n2_trenda, n2_ymina, n2_ymaxa)

```
```{r}
#WRF A
#plot smooth frames
p_wrf_a <- plotly::plot_ly() %>%
  plotly::add_lines(x = ~date_vec_n1a, y = ~n1_trenda,
                    data = smooth_frame_n1a,
                    hoverinfo = "text",
                    text = ~paste('</br> Date: ', date_vec_n1a,
                                  '</br> Median Log Copies: ', round(n1_trenda, digits = 2),
                                  '</br> Target: N1'),
                    line = list(color = '#1B9E77', size = 8, opacity = 0.65),
                    showlegend = FALSE) %>%
     layout(xaxis = list(range = c(mindate - 7, maxdate + 7))) %>% #buffer here
plotly::add_lines(x = ~date_vec_n2a, y = ~n2_trenda,
                  data = smooth_frame_n2a,
                    hoverinfo = "text",
                    text = ~paste('</br> Date: ', date_vec_n2a,
                                  '</br> Median Log Copies: ', round(n2_trenda, digits = 2),
                                  '</br> Target: N2'),
                    line = list(color = '#D95F02', size = 8, opacity = 0.65),
                    showlegend = FALSE) %>%
plotly::add_ribbons(x ~date_vec_n1a, ymin = ~n1_ymina, ymax = ~n1_ymaxa,
                    showlegend = FALSE,
                    opacity = 0.25,
                    hoverinfo = "text",
                    text = ~paste('</br> Date: ', date_vec_n1a, #leaving in case we want to change
                                  '</br> Max Log Copies: ', round(n1_ymaxa, digits = 2),
                                  '</br> Min Log Copies: ', round(n1_ymina, digits = 2),
                                  '</br> Target: N1'),
                    name = "",
                    line = list(color = '#1B9E77')) %>%
plotly::add_ribbons(x ~date_vec_n2a, ymin = ~n2_ymina, ymax = ~n2_ymaxa,
                    showlegend = FALSE,
                    opacity = 0.25,
                    hoverinfo = "text",
                    text = ~paste('</br> Date: ', date_vec_n2a, #leaving in case we want to change
                                  '</br> Max Log Copies: ', round(n2_ymaxa, digits = 2),
                                  '</br> Min Log Copies: ', round(n2_ymina, digits = 2),
                                  '</br> Target: N2'),
                    name = "",
                    line = list(color = '#D95F02')) %>%
                layout(yaxis = list(title = "Total Log SARS CoV-2 Copies", 
                                 showline = TRUE,
                                 automargin = TRUE)) %>%
                layout(xaxis = list(title = "Date")) %>%
                layout(title = "WRF A") %>%
    plotly::add_segments(x = as.Date("2020-06-24"), 
                                          xend = as.Date("2020-06-24"), 
                                          y = ~min(n1_ymina), yend = ~max(n1_ymaxa),
                                          opacity = 0.35,
                                          name = "Bars Repoen",
                                          hoverinfo = "text",
                                          text = "</br> Bars Reopen",
                                                 "</br> 2020-06-24",
                                          showlegend = FALSE,
                                          line = list(color = "black", dash = "dash")) %>%
    plotly::add_segments(x = as.Date("2020-07-09"), 
                                          xend = as.Date("2020-07-09"), 
                                          y = ~min(n1_ymina), yend = ~max(n1_ymaxa),
                                          opacity = 0.35,
                                          name = "Mask Mandate",
                                          hoverinfo = "text",
                                          text = "</br> Mask Mandate",
                                                 "</br> 2020-07-09",
                                          showlegend = FALSE,
                                          line = list(color = "black", dash = "dash")) %>%
    plotly::add_segments(x = as.Date("2020-08-20"), 
                                          xend = as.Date("2020-08-20"), 
                                          y = ~min(n1_ymina), yend = ~max(n1_ymaxa),
                                          opacity = 0.35,
                                          name = "</br> Classes Begin",
                                                 "</br> 2020-08-20",
                                          hoverinfo = "text",
                                          text = "Classes Begin",
                                          showlegend = FALSE,
                                          line = list(color = "black", dash = "dash")) %>%
        plotly::add_segments(x = as.Date("2020-10-03"), 
                                          xend = as.Date("2020-10-03"), 
                                          y = ~min(n1_ymina), yend = ~max(n1_ymaxa),
                                          opacity = 0.35,
                                          name = "</br> First Home Football Game",
                                                 "</br> 2020-10-03",
                                          hoverinfo = "text",
                                          text = "First Home Football Game",
                                          showlegend = FALSE,
                                          line = list(color = "black", dash = "dash")) %>%
  plotly::add_markers(x = ~date, y = ~log_sum_copies_L,
                      data = wrfa_smooth_n1,
                       hoverinfo = "text",
                       showlegend = FALSE,
                       text = ~paste('</br> Date: ', date, 
                                     '</br> Actual Log Copies: ', round(log_sum_copies_L, digits = 2)),
                       marker = list(color = '#1B9E77', size = 6, opacity = 0.65)) %>%
    plotly::add_markers(x = ~date, y = ~log_sum_copies_L,
                      data = wrfa_smooth_n2,
                       hoverinfo = "text",
                       showlegend = FALSE,
                       text = ~paste('</br> Date: ', date, 
                                     '</br> Actual Log Copies: ', round(log_sum_copies_L, digits = 2)),
                       marker = list(color = '#D95F02', size = 6, opacity = 0.65))

p_wrf_a
```

```{r}
save(p_wrf_a, file = "./plotly_objs/p_wrf_a.rda")
```

```{r}
#**************************************WRF B PLOT**********************************************
#add trendlines 
#extract data from geom_smooth
#n1 extract
# *********************************span 0.6***********************************
#*****************Must always update the n = TOTAL NUMBER OF DAYS*************************
extract_n1b <- ggplot(wrfb_smooth_n1, aes(x = date, y = log_sum_copies_L)) + 
  stat_smooth(aes(outfit=fit_n1b<<-..y..), method = "loess", color = '#1B9E77', 
              span = 0.6, n = 142)
#n2 extract
extract_n2b <- ggplot(wrfb_smooth_n2, aes(x = date, y = log_sum_copies_L)) + 
  stat_smooth(aes(outfit=fit_n2b<<-..y..), method = "loess", color = '#1B9E77', 
              span = 0.6, n = 142)

#look at the fits to align dates and total observations
#n1
extract_n1b
fit_n1b
#n2
extract_n2b
fit_n2b

#assign fits to a vector
n1_trendb <- fit_n1b
n2_trendb <- fit_n2b

#extract y min and max for each
limits_n1b <- ggplot_build(extract_n1b)$data
limits_n1b <- as.data.frame(limits_n1b)
n1_yminb <- limits_n1b$ymin
n1_ymaxb <- limits_n1b$ymax

limits_n2b <- ggplot_build(extract_n2b)$data
limits_n2b <- as.data.frame(limits_n2b)
n2_yminb <- limits_n2b$ymin
n2_ymaxb <- limits_n2b$ymax

#reassign dataframes (just to be safe)
work_n1b <- wrfb_smooth_n1
work_n2b<- wrfb_smooth_n1

#fill in missing dates to smooth fits
work_n1b <- work_n1b %>% complete(date = seq(min(date), max(date), by = "1 day"))
date_vec_n1b <- work_n1b$date
work_n2b <- work_n2b %>% complete(date = seq(min(date), max(date), by = "1 day"))
date_vec_n2b <- work_n2b$date

#create a new smooth dataframe to layer
smooth_frame_n1b <- data.frame(date_vec_n1b, n1_trendb, n1_yminb, n1_ymaxb)
smooth_frame_n2b <- data.frame(date_vec_n2b, n2_trendb, n2_yminb, n2_ymaxb)

#WRF B
#plot smooth frames
p_wrf_b <- plotly::plot_ly() %>%
  plotly::add_lines(x = ~date_vec_n1b, y = ~n1_trendb,
                    data = smooth_frame_n1b,
                    hoverinfo = "text",
                    text = ~paste('</br> Date: ', date_vec_n1b,
                                  '</br> Median Log Copies: ', round(n1_trendb, digits = 2),
                                  '</br> Target: N1'),
                    line = list(color = '#1B9E77', size = 8, opacity = 0.65),
                    showlegend = FALSE) %>%
     layout(xaxis = list(range = c(mindate - 7, maxdate + 7))) %>% #buffer here
plotly::add_lines(x = ~date_vec_n2b, y = ~n2_trendb,
                  data = smooth_frame_n2b,
                    hoverinfo = "text",
                    text = ~paste('</br> Date: ', date_vec_n2b,
                                  '</br> Median Log Copies: ', round(n2_trendb, digits = 2),
                                  '</br> Target: N2'),
                    line = list(color = '#D95F02', size = 8, opacity = 0.65),
                    showlegend = FALSE) %>%
plotly::add_ribbons(x ~date_vec_n1b, ymin = ~n1_yminb, ymax = ~n1_ymaxb,
                    showlegend = FALSE,
                    opacity = 0.25,
                    hoverinfo = "text",
                    text = ~paste('</br> Date: ', date_vec_n1b, #leaving in case we want to change
                                  '</br> Max Log Copies: ', round(n1_ymaxb, digits = 2),
                                  '</br> Min Log Copies: ', round(n1_yminb, digits = 2),
                                  '</br> Target: N1'),
                    name = "",
                    line = list(color = '#1B9E77')) %>%
plotly::add_ribbons(x ~date_vec_n2b, ymin = ~n2_yminb, ymax = ~n2_ymaxb,
                    showlegend = FALSE,
                    opacity = 0.25,
                    hoverinfo = "text",
                    text = ~paste('</br> Date: ', date_vec_n2b, #leaving in case we want to change
                                  '</br> Max Log Copies: ', round(n2_ymaxb, digits = 2),
                                  '</br> Min Log Copies: ', round(n2_yminb, digits = 2),
                                  '</br> Target: N2'),
                    name = "",
                    line = list(color = '#D95F02')) %>%
                layout(yaxis = list(title = "Total Log SARS CoV-2 Copies", 
                                 showline = TRUE,
                                 automargin = TRUE)) %>%
                layout(xaxis = list(title = "Date")) %>%
                layout(title = "WRF B") %>%
    plotly::add_segments(x = as.Date("2020-06-24"), 
                                          xend = as.Date("2020-06-24"), 
                                          y = ~min(n1_yminb), yend = ~max(n1_ymaxb),
                                          opacity = 0.35,
                                          name = "Bars Repoen",
                                          hoverinfo = "text",
                                          text = "</br> Bars Reopen",
                                                 "</br> 2020-06-24",
                                          showlegend = FALSE,
                                          line = list(color = "black", dash = "dash")) %>%
    plotly::add_segments(x = as.Date("2020-07-09"), 
                                          xend = as.Date("2020-07-09"), 
                                          y = ~min(n1_yminb), yend = ~max(n1_ymaxb),
                                          opacity = 0.35,
                                          name = "Mask Mandate",
                                          hoverinfo = "text",
                                          text = "</br> Mask Mandate",
                                                 "</br> 2020-07-09",
                                          showlegend = FALSE,
                                          line = list(color = "black", dash = "dash")) %>%
    plotly::add_segments(x = as.Date("2020-08-20"), 
                                          xend = as.Date("2020-08-20"), 
                                          y = ~min(n1_yminb), yend = ~max(n1_ymaxb),
                                          opacity = 0.35,
                                          name = "</br> Classes Begin",
                                                 "</br> 2020-08-20",
                                          hoverinfo = "text",
                                          text = "Classes Begin",
                                          showlegend = FALSE,
                                          line = list(color = "black", dash = "dash")) %>%
        plotly::add_segments(x = as.Date("2020-10-03"), 
                                          xend = as.Date("2020-10-03"), 
                                          y = ~min(n1_yminb), yend = ~max(n1_ymaxb),
                                          opacity = 0.35,
                                          name = "</br> First Home Football Game",
                                                 "</br> 2020-10-03",
                                          hoverinfo = "text",
                                          text = "First Home Football Game",
                                          showlegend = FALSE,
                                          line = list(color = "black", dash = "dash")) %>%
  plotly::add_markers(x = ~date, y = ~log_sum_copies_L,
                      data = wrfb_smooth_n1,
                       hoverinfo = "text",
                       showlegend = FALSE,
                       text = ~paste('</br> Date: ', date, 
                                     '</br> Actual Log Copies: ', round(log_sum_copies_L, digits = 2)),
                       marker = list(color = '#1B9E77', size = 6, opacity = 0.65)) %>%
    plotly::add_markers(x = ~date, y = ~log_sum_copies_L,
                      data = wrfb_smooth_n2,
                       hoverinfo = "text",
                       showlegend = FALSE,
                       text = ~paste('</br> Date: ', date, 
                                     '</br> Actual Log Copies: ', round(log_sum_copies_L, digits = 2)),
                       marker = list(color = '#D95F02', size = 6, opacity = 0.65))

p_wrf_b
```

```{r}
save(p_wrf_b, file = "./plotly_objs/p_wrf_b.rda")
```




#**************************************WRF C PLOT********************************************** Does not work until raw data fixed
#add trendlines 
#extract data from geom_smooth
#n1 extract
# *********************************span 0.6***********************************
#*****************Must always update the n = TOTAL NUMBER OF DAYS*************************

```{r}
extract_n1c <- ggplot(wrfc_smooth_n1, aes(x = date, y = log_sum_copies_L)) + 
  stat_smooth(aes(outfit=fit_n1c<<-..y..), method = "loess", color = '#1B9E77', 
              span = 0.6, n = 128)
#n2 extract
extract_n2c <- ggplot(wrfc_smooth_n2, aes(x = date, y = log_sum_copies_L)) + 
  stat_smooth(aes(outfit=fit_n2c<<-..y..), method = "loess", color = '#1B9E77', 
              span = 0.6, n = 128)

#look at the fits to align dates and total observations
#n1
extract_n1c
fit_n1c
#n2
extract_n2c
fit_n2c

#assign fits to a vector
n1_trendc <- fit_n1c
n2_trendc <- fit_n2c

#extract y min and max for each
limits_n1c <- ggplot_build(extract_n1c)$data
limits_n1c <- as.data.frame(limits_n1c)
n1_yminc <- limits_n1c$ymin
n1_ymaxc <- limits_n1c$ymax

limits_n2c <- ggplot_build(extract_n2c)$data
limits_n2c <- as.data.frame(limits_n2c)
n2_yminc <- limits_n2c$ymin
n2_ymaxc <- limits_n2c$ymax

#reassign dataframes (just to be safe)
work_n1c <- wrfc_smooth_n1
work_n2c <- wrfc_smooth_n1

#fill in missing dates to smooth fits
work_n1c <- work_n1c %>% complete(date = seq(min(date), max(date), by = "1 day"))
date_vec_n1c <- work_n1c$date
work_n2c <- work_n2c %>% complete(date = seq(min(date), max(date), by = "1 day"))
date_vec_n2c <- work_n2c$date

#create a new smooth dataframe to layer
smooth_frame_n1c <- data.frame(date_vec_n1c, n1_trendc, n1_yminc, n1_ymaxc)
smooth_frame_n2c <- data.frame(date_vec_n2c, n2_trendc, n2_yminc, n2_ymaxc)


#WRF C
#plot smooth frames
p_wrf_c <- plotly::plot_ly() %>%
  plotly::add_lines(x = ~date_vec_n1c, y = ~n1_trendc,
                    data = smooth_frame_n1c,
                    hoverinfo = "text",
                    text = ~paste('</br> Date: ', date_vec_n1c,
                                  '</br> Median Log Copies: ', round(n1_trendc, digits = 2),
                                  '</br> Target: N1'),
                    line = list(color = '#1B9E77', size = 8, opacity = 0.65),
                    showlegend = FALSE) %>%
   layout(xaxis = list(range = c(mindate - 7, maxdate + 7))) %>% #buffer here
plotly::add_lines(x = ~date_vec_n2c, y = ~n2_trendc,
                  data = smooth_frame_n2c,
                    hoverinfo = "text",
                    text = ~paste('</br> Date: ', date_vec_n2c,
                                  '</br> Median Log Copies: ', round(n2_trendc, digits = 2),
                                  '</br> Target: N2'),
                    line = list(color = '#D95F02', size = 8, opacity = 0.65),
                    showlegend = FALSE) %>%
plotly::add_ribbons(x ~date_vec_n1c, ymin = ~n1_yminc, ymax = ~n1_ymaxc,
                    showlegend = FALSE,
                    opacity = 0.25,
                    hoverinfo = "text",
                    text = ~paste('</br> Date: ', date_vec_n1c, #leaving in case we want to change
                                  '</br> Max Log Copies: ', round(n1_ymaxc, digits = 2),
                                  '</br> Min Log Copies: ', round(n1_yminc, digits = 2),
                                  '</br> Target: N1'),
                    name = "",
                    line = list(color = '#1B9E77')) %>%
plotly::add_ribbons(x ~date_vec_n2c, ymin = ~n2_yminc, ymax = ~n2_ymaxc,
                    showlegend = FALSE,
                    opacity = 0.25,
                    hoverinfo = "text",
                    text = ~paste('</br> Date: ', date_vec_n2c, #leaving in case we want to change
                                  '</br> Max Log Copies: ', round(n2_ymaxc, digits = 2),
                                  '</br> Min Log Copies: ', round(n2_yminc, digits = 2),
                                  '</br> Target: N2'),
                    name = "",
                    line = list(color = '#D95F02')) %>%
                layout(yaxis = list(title = "Total Log SARS CoV-2 Copies", 
                                 showline = TRUE,
                                 automargin = TRUE)) %>%
                layout(xaxis = list(title = "Date")) %>%
                layout(title = "WRF C") %>%
    plotly::add_segments(x = as.Date("2020-06-24"), 
                                          xend = as.Date("2020-06-24"), 
                                          y = ~min(n1_yminc), yend = ~max(n1_ymaxc),
                                          opacity = 0.35,
                                          name = "Bars Repoen",
                                          hoverinfo = "text",
                                          text = "</br> Bars Reopen",
                                                 "</br> 2020-06-24",
                                          showlegend = FALSE,
                                          line = list(color = "black", dash = "dash")) %>%
    plotly::add_segments(x = as.Date("2020-07-09"), 
                                          xend = as.Date("2020-07-09"), 
                                          y = ~min(n1_yminc), yend = ~max(n1_ymaxc),
                                          opacity = 0.35,
                                          name = "Mask Mandate",
                                          hoverinfo = "text",
                                          text = "</br> Mask Mandate",
                                                 "</br> 2020-07-09",
                                          showlegend = FALSE,
                                          line = list(color = "black", dash = "dash")) %>%
    plotly::add_segments(x = as.Date("2020-08-20"), 
                                          xend = as.Date("2020-08-20"), 
                                          y = ~min(n1_yminc), yend = ~max(n1_ymaxc),
                                          opacity = 0.35,
                                          name = "</br> Classes Begin",
                                                 "</br> 2020-08-20",
                                          hoverinfo = "text",
                                          text = "Classes Begin",
                                          showlegend = FALSE,
                                          line = list(color = "black", dash = "dash")) %>%
        plotly::add_segments(x = as.Date("2020-10-03"), 
                                          xend = as.Date("2020-10-03"), 
                                          y = ~min(n1_yminc), yend = ~max(n1_ymaxc),
                                          opacity = 0.35,
                                          name = "</br> First Home Football Game",
                                                 "</br> 2020-10-03",
                                          hoverinfo = "text",
                                          text = "First Home Football Game",
                                          showlegend = FALSE,
                                          line = list(color = "black", dash = "dash")) %>%
  plotly::add_markers(x = ~date, y = ~log_sum_copies_L,
                      data = wrfc_smooth_n1,
                       hoverinfo = "text",
                       showlegend = FALSE,
                       text = ~paste('</br> Date: ', date, 
                                     '</br> Actual Log Copies: ', round(log_sum_copies_L, digits = 2)),
                       marker = list(color = '#1B9E77', size = 6, opacity = 0.65)) %>%
    plotly::add_markers(x = ~date, y = ~log_sum_copies_L,
                      data = wrfc_smooth_n2,
                       hoverinfo = "text",
                       showlegend = FALSE,
                       text = ~paste('</br> Date: ', date, 
                                     '</br> Actual Log Copies: ', round(log_sum_copies_L, digits = 2)),
                       marker = list(color = '#D95F02', size = 6, opacity = 0.65))

p_wrf_c

```

```{r}
save(p_wrf_c, file = "./plotly_objs/p_wrf_c.rda")
```


```{r}
save(smooth_frame_n1a, file = "./plotly_objs/smooth_frame_n1a.rda")
save(smooth_frame_n2a, file = "./plotly_objs/smooth_frame_n2a.rda")
save(smooth_frame_n1b, file = "./plotly_objs/smooth_frame_n1b.rda")
save(smooth_frame_n2b, file = "./plotly_objs/smooth_frame_n2b.rda")
save(smooth_frame_n1c, file = "./plotly_objs/smooth_frame_n1c.rda")
save(smooth_frame_n2c, file = "./plotly_objs/smooth_frame_n2c.rda")

```

```{r}
save(date_vec_n1a, file = "./plotly_objs/date_vec_n1a.rda")
save(date_vec_n2a, file = "./plotly_objs/date_vec_n2a.rda")
save(date_vec_n1b, file = "./plotly_objs/date_vec_n1b.rda")
save(date_vec_n2b, file = "./plotly_objs/date_vec_n2b.rda")
save(date_vec_n1c, file = "./plotly_objs/date_vec_n1c.rda")
save(date_vec_n2c, file = "./plotly_objs/date_vec_n2c.rda")
```

```{r}
save(n1_ymina, file = "./plotly_objs/n1_ymina.rda")
save(n1_ymaxa, file = "./plotly_objs/n1_ymaxa.rda")
save(n2_ymina, file = "./plotly_objs/n2_ymina.rda")
save(n2_ymaxa, file = "./plotly_objs/n2_ymaxa.rda")

save(n1_yminb, file = "./plotly_objs/n1_yminb.rda")
save(n1_ymaxb, file = "./plotly_objs/n1_ymaxb.rda")
save(n2_yminb, file = "./plotly_objs/n2_yminb.rda")
save(n2_ymaxb, file = "./plotly_objs/n2_ymaxb.rda")

save(n1_yminc, file = "./plotly_objs/n1_yminc.rda")
save(n1_ymaxc, file = "./plotly_objs/n1_ymaxc.rda")
save(n2_yminc, file = "./plotly_objs/n2_yminc.rda")
save(n2_ymaxc, file = "./plotly_objs/n2_ymaxc.rda")

```



